Ms 1

### 2018-01-31 ms1/ms1_display.Rmd
a few more displays

The change in overall use is so small that I'll give it another decimal place:

```{r}
claims_by_abx %>%
  filter(abx=='pde', year %in% c(2011, 2015)) %>%
  select(year, cpkp) %>%
  mutate(cpkp=round(cpkp, 1)) %>%
  kable(caption='Overall use')
```

>>>>

The changes in overall use and appropriate use are so small that I'll give it another decimal place:

```{r}
# N.B.: 2015 claims were adjusted during loading of the data file
claims_by_abx %>%
  filter(abx %in% c('pde', 'pde_approp'), year %in% c(2011, 2015)) %>%
  select(year, abx, cpkp) %>%
  mutate(cpkp=round(cpkp, 1)) %>%
  spread(year, cpkp) %>%
  kable(caption='CPKP for small changes')
```
